Methods and Results

### 2021-08-07 ms.Rmd
Minor change

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```

>>>>

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: false
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---
```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
    ## and rounded to 2 digits      ## and rounded to 2 digits
    options(digits = 2)
```
